---
title: "CRISP Data Anlaysis"
author: "Michael Doerfler"
date: "2025-07-15"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(here)
source(here::here("./01_functions.R"))
```

The following RMarkdown document provides the code for the real-data analysis on the CRISP data.

n15: Sampled in both streams, tested negative, or sampled in 2 but not 1, tested negative.

n2: Sampled in both streams, tested positive.

n4: Sampled in 1 but not 2, tested positive.

n6: Sampled in 2 but not 1, tested positive.

n37: Not sampled in either stream OR sampled in 1 but not 2, tested negative.

There were 3 cells with Anchor=1, AnchorRecurrence=0, and CoCValidatedRecurrence=1. We move these 3 observations into the n15 cell.

Our data are:

n15: 169

n2: 12

n4: 52

n6: 19

n37: 777

As a double check, we make sure these add up to 1029 (the total number of patients).

```{r}
data<-c(169, 12, 52, 19, 777)
sum(data)
```
Here we get our point estimates and standard errors.

```{r}

five_cell_estimator(data=data, type="Unadjusted", psi=200/1029)
five_cell_estimator(data=data, type="FPC1", psi=200/1029)
five_cell_estimator(data=data, type="FPC2", psi=200/1029)


rs_estimator(data=data, type="Unadjusted")
rs_estimator(data=data, type="FPC")

chapman_estimator(data=data)

```

Here we get our confidence intervals.

```{r}
set.seed(1234)

est5<-five_cell_estimator(data=data, type="Unadjusted", psi=200/1029)$est #Extracting point estimate for use with Wald interval.
se5<-five_cell_estimator(data=data, type="Unadjusted", psi=200/1029)$se #Extracting standard error for use with Wald interval.

se5_FPC1<-five_cell_estimator(data=data, type="FPC1", psi=200/1029)$se #Extracting FPC1 adjusted standard error for use with Wald interval.

se5_FPC2<-five_cell_estimator(data=data, type="FPC2", psi=200/1029)$se #Extracting FPC2 adjusted standard error for use with Wald interval.

est_rs<-rs_estimator(data=data)$est

se_rs<-rs_estimator(data=data, type="Unadjusted")$se

se_rs_FPC<-rs_estimator(data=data, type="FPC")$se


##Creating Wald CIs for 5 cell MLE
wald_ci2(est5, se5, alpha=0.05, Ntot=1029, n15=169, nc=83)

wald_ci2(est5, se5_FPC1, alpha=0.05, Ntot=1029, n15=169, nc=83)

wald_ci2(est5, se5_FPC2, alpha=0.05, Ntot=1029, n15=169, nc=83)

#Bayes CIs for 5 cell MLE

bayes_ci_5(data=data, alpha=0.05, type="Unadjusted", postdraws=10000)

bayes_ci_5(data=data, alpha=0.05, type="FPC1", postdraws=10000, psi=200/1029)

bayes_ci_5(data=data, alpha=0.05, type="FPC2", postdraws=10000, psi=200/1029)

#Wald CIs for RS

wald_ci2(est_rs, se_rs, alpha=0.05, Ntot=1029, n15=169, nc=83)

wald_ci2(est_rs, se_rs_FPC, alpha=0.05, Ntot=1029, n15=169, nc=83)

bayes_ci_rs(data=data, alpha=0.05, type="FPC")

#Chapman CI

sadinle_ci(data=data, alpha=0.05)

rivest(data=data, alpha=0.05)




```